---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Explore Infectious Disease Models

[This shiny app](http://seabbs.co.uk/shiny/exploreidmodels) allows interactive exploration of a dynamic infections disease models abstracted from the required code implementation. Model code is provided so that users can develop there own more compelx models from these basic frameworks.  

## Installing the shiny app locally


## Manual Install

To install and run the shiny app locally on your own computer you will need to first install [R](https://www.r-project.org/), it is also suggested that you install [Rstudio](https://www.rstudio.com/products/rstudio/download/). After downloading the source code from [this repository](https://www.github.com/seabbs/exploreidmodels) click on the `exploreidmodels.Rprof` file, this will open an Rstudio window. Type the following code into the command line;

```{r, eval = FALSE}
install.packages("shiny")
install.packages("shinydashboard")
install.packages("shinyBS")
install.packages("tidyverse")
install.packages("rmarkdown")
```

To run the app open the `ui.R` file and press run, depending on your computer this may take some time.


### Using Docker

[Docker](https://www.docker.com/what-docker) is a container software that seeks to eliminate "works on my machine" issues. For installation and set up instructions see [here](https://www.docker.com/community-edition). 

This docker container is based on the [shiny](https://hub.docker.com/r/rocker/shiny/) docker image, see [here](https://github.com/rocker-org/shiny) for instructions on use. To run the docker image run the following in a bash shell:

```{bash, eval = FALSE}
docker pull seabbs/exploreidmodels
docker run --rm -p 3838:3838 seabbs/exploreidmodels
```

The shiny server can be found on port `:3838` at your local machines ip (or localhost on windows), fcdashboard can be found at `your-ip:3838/exploreidmodels`.



